Manuscript draft

### 2019-06-28 manuscript/manuscript draft.Rmd
updated manuscript draft

| Variable | Definition | Components included | Methodologies used | Number of records | Number of plots |
|--------------|-------------------|-------------|------------------------|-------|-------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 254 | 91 |
| NPP | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root and optionally understory | Direct measurement of annual increments of components | 116 | 85 |
| ANPP | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 259 | 170 |
| ANPP~foliage~ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 100 | 96 |
| ANPP~woodystem~ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 252 |
| BNPP~root~ | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures | 105 | 90 |
| BNPP~rootfine~ | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 96 | 88 |
| R~auto~ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 22 |
| R~autoroot~ | Annual root respiration | Coarse and fine roots | Measurement of root gas exchange | 57 | 38 |

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Graph to show primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("effect_of_latitude.png")
```

Latitude is a strong predictor for many of the carbon fluxes, explaining ~70% of variation in GPP (n = 241, p<0.01), 64% in NPP (n = 109, p<0.01) and 60% in ANPP (n = 252, p<0.01).

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots show smaller component fluxes (1) and (2); the larger flux (3) defined by the combination of (1) and (2); and a modelled estimate of the sum of (1) and (2). 95\\% confidence intervals are plotted for (3).", fig.pos='H'}

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Ratio of ANPP foliage to ANPP woody and ANPP woody stem plotted against major ecozones. All pairwise comparisons are significant. Significance levels of pairwise comparisons are indicated where * $p \\leq 0.05 $; ** $p \\leq 0.01 $; *** $p \\leq 0.001 $; **** $p \\leq 0.0001 $.", fig.pos='H'}
  knitr::include_graphics("boxplot_foliage_woody_combined.png")
```

>>>>

| Variable | Definition | Components included | Methodologies used | Number of records | Number of plots |
|--------------|-------------------|-------------|------------------------|-------|-------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 254 | 91 |
| NPP | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root and optionally understory | Direct measurement of annual increments of components | 116 | 85 |
| ANPP | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 259 | 170 |
| ANPP~foliage~ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 100 | 96 |
| ANPP~woodystem~ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 252 |
| BNPP~root~ | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures | 105 | 90 |
| BNPP~rootfine~ | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 96 | 88 |
| R~auto~ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 22 |
| R~root~ | Annual root respiration | Coarse and fine roots | Measurement of root gas exchange | 57 | 38 |

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Graphs to show primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("effect_of_latitude.png")
```

Latitude is a strong predictor for many of the carbon fluxes, explaining ~65% of variation in GPP (n = 254, p<0.01), 51% in NPP (n = 116, p<0.01) and 50% in ANPP (n = 259, p<0.01).

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots 1 - 3 show two component fluxes; a larger flux, defined as the combination of the two component fluxes; and a modelled estimate of the sum of the two component fluxes. 95\\% confidence intervals are plotted for the larger flux. Plot 4 shows three belowground fluxes, and a modelled estimate of the total belowground carbon flux", fig.pos='H'}

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Ratio of ANPP foliage to ANPP woody stem plotted against major ecozones. All pairwise comparisons are significant. Significance levels of pairwise comparisons are indicated where * $p \\leq 0.05 $; ** $p \\leq 0.01 $; *** $p \\leq 0.001 $; **** $p \\leq 0.0001 $.", fig.pos='H'}
  knitr::include_graphics("boxplot_foliage_woodystem.png")
```
